---
format:
  pdf:
    toc: false
    number-sections: false
    highlight-style: haddock
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    mainfont: Avenir
    sansfont: Avenir
    fontsize: 10pt
    geometry:
      - margin=1in
      - heightrounded
    include-in-header:
      text: |
        \usepackage{xcolor}
        \definecolor{gis}{HTML}{E69F00}
        \definecolor{health}{HTML}{56B4E9}
        \definecolor{innovation}{HTML}{CC79A7}
        \definecolor{labor}{HTML}{B8860B}
        \definecolor{operations}{HTML}{0072B2}
        \definecolor{policy}{HTML}{D55E00}
        \definecolor{sustainability}{HTML}{009E73}
        \definecolor{event}{HTML}{17A2B8}
        \definecolor{awardgold}{HTML}{B8860B}
        \definecolor{gwblue}{HTML}{033C5A}
        \definecolor{gwgold}{HTML}{AA9144}
        \definecolor{lightgray}{HTML}{F5F5F5}
        \definecolor{darkgray}{HTML}{444444}
        \usepackage{mdframed}
        \usepackage{fontawesome5}
        \usepackage{tabularx}
        \usepackage{wrapfig}
        \usepackage{scrlayer-scrpage}
        \pagestyle{scrheadings}
        \clearpairofpagestyles
        \lohead{\small\textit{\leftmark}}
        \cofoot[{\makebox[0pt][c]{\smash{\raisebox{16pt}{\rule{\textwidth}{0.4pt}}}}\pagemark}]{\makebox[0pt][c]{\smash{\raisebox{16pt}{\rule{\textwidth}{0.4pt}}}}\pagemark}
        \addtolength{\footskip}{8pt}
        \KOMAoptions{headsepline=true}
        \AtBeginDocument{\hypersetup{pdfpagemode=UseOutlines, bookmarksdepth=-1}\thispagestyle{empty}}
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup
library(tidyverse)
library(knitr)

# Read submissions data with type information
submissions <- read_csv(
  file.path('data', 'submissions.csv'),
  show_col_types = FALSE
) %>%
  mutate(id = as.character(id))

# Read self-organized panel details
self_sessions <- read_csv(
  file.path('data', 'self-sessions.csv'),
  show_col_types = FALSE
) %>%
  mutate(id = as.character(id))

# Read standalone panel sessions (these are interwoven into the schedule
# as panel discussion blocks, separate from paper sessions)
panels_raw <- read_csv(
  file.path('data', 'panels.csv'),
  show_col_types = FALSE
) %>%
  mutate(
    date_parsed = lubridate::mdy(date),
    day_name = case_when(
      date_parsed == as.Date("2026-06-03") ~ "Wednesday",
      date_parsed == as.Date("2026-06-04") ~ "Thursday",
      date_parsed == as.Date("2026-06-05") ~ "Friday",
      TRUE ~ format(date_parsed, "%A")
    ),
    start_dt = as.POSIXct(
      paste(format(date_parsed, "%Y-%m-%d"), time_start),
      format = "%Y-%m-%d %H:%M:%S"
    ),
    end_dt = as.POSIXct(
      paste(format(date_parsed, "%Y-%m-%d"), time_end),
      format = "%Y-%m-%d %H:%M:%S"
    ),
    room = str_trim(str_replace_all(room, "\\s+", " ")),
    track_color = case_when(
      category == "General Industry Studies" ~ "gis",
      category ==
        "Health Care Systems, Biotechnology, and Pharmaceuticals" ~ "health",
      category ==
        "Innovation, Entrepreneurship, and AI-Driven Transformation" ~ "innovation",
      category ==
        "Labor Markets, Organizations, and the Future of Work" ~ "labor",
      category ==
        "Operations, Supply Chain, and AI-Enhanced Industry 4.0" ~ "operations",
      category == "Public Policy and Global Competitiveness" ~ "policy",
      category ==
        "Sustainable Innovation, Energy, and Mobility" ~ "sustainability",
      TRUE ~ "black"
    )
  )

# Read full schedule (with time/room assignments)
schedule <- read_csv(
  file.path('data', 'schedule.csv'),
  show_col_types = FALSE
) %>%
  mutate(id = as.character(id))

# Paper order is stored in schedule.csv (carried from session CSVs)
# No need to recompute from row position.

# Merge submissions with schedule (paper_order comes from schedule.csv)
sessions <- submissions %>%
  inner_join(schedule, by = "id") %>%
  mutate(
    id = as.character(id),
    session_id = as.character(session_id),
    is_self_organized = type == "self_organized_panel",
    panel_description = NA_character_
  )

# One discussant per self-organized session (first non-empty value)
self_discussants <- self_sessions %>%
  group_by(id) %>%
  summarize(
    discussant = first(discussant[
      !is.na(discussant) & str_trim(discussant) != ""
    ]),
    .groups = "drop"
  )

# Add self-organized panel papers to sessions
# These papers share the same session_id as their parent panel submission.
# paper_order comes from the paper_order column in self-sessions.csv.
self_papers <- self_sessions %>%
  select(
    parent_id = id,
    authors,
    author_names,
    title,
    abstract,
    paper_order
  ) %>%
  left_join(self_discussants, by = c("parent_id" = "id")) %>%
  left_join(
    sessions %>%
      filter(is_self_organized) %>%
      distinct(
        id,
        session_id,
        session_name,
        time_slot,
        room,
        date,
        day,
        start_time,
        end_time,
        time_order,
        category,
        type
      ),
    by = c("parent_id" = "id")
  ) %>%
  mutate(
    is_panel = FALSE,
    is_self_organized = FALSE
  )

# Replace self-organized panel entries with their constituent papers
sessions <- sessions %>%
  filter(!is_self_organized) %>%
  mutate(discussant = NA_character_) %>%
  bind_rows(self_papers %>% select(-parent_id))

# is_panel is always FALSE (no panel_discussion type submissions)
sessions <- sessions %>%
  mutate(
    is_panel = if_else(is.na(is_panel), FALSE, is_panel)
  )

# Read overview events (breaks, meals, receptions, etc.)
covered_sessions <- c(
  "Paper Sessions",
  "Opening Plenary",
  "Concurrent Panel Sessions"
)

overview_events <- read_csv(
  file.path('data', 'overview.csv'),
  show_col_types = FALSE,
  col_types = cols(.default = "c")
) %>%
  rename_with(str_trim) %>%
  rename(
    weekday = Weekday,
    time_start_str = `Time Start`,
    time_end_str = `Time End`,
    session = Session,
    building = Building,
    room_raw = Room
  ) %>%
  mutate(
    weekday = str_trim(weekday),
    time_start_str = str_trim(time_start_str),
    time_end_str = str_trim(time_end_str),
    session = str_trim(session)
  ) %>%
  filter(!session %in% covered_sessions) %>%
  mutate(
    date_parsed = case_when(
      weekday == "Wednesday" ~ as.Date("2026-06-03"),
      weekday == "Thursday" ~ as.Date("2026-06-04"),
      weekday == "Friday" ~ as.Date("2026-06-05")
    ),
    day_name = weekday,
    room = str_trim(paste(
      building,
      str_trim(str_replace_all(room_raw, "\\s+", " ")),
      sep = ", "
    )),
    start_dt = as.POSIXct(
      paste(format(date_parsed, "%Y-%m-%d"), time_start_str),
      format = "%Y-%m-%d %I:%M %p"
    ),
    end_dt = as.POSIXct(
      paste(format(date_parsed, "%Y-%m-%d"), time_end_str),
      format = "%Y-%m-%d %I:%M %p"
    ),
    session_name = session
  )

# Helper function to escape LaTeX special characters
escape_latex <- function(text) {
  if (is.na(text) || nchar(text) == 0) {
    return(text)
  }
  text <- str_replace_all(text, "\\\\", "\\\\textbackslash{}")
  text <- str_replace_all(text, "([&%$#_{}])", "\\\\\\1")
  text <- str_replace_all(text, "\\^", "\\\\textasciicircum{}")
  text <- str_replace_all(text, "~", "\\\\textasciitilde{}")
  return(text)
}

# Return the full "Name (Affiliation)" entry for the presenting author (*) of the first paper.
# Falls back to the first author if no * is marked.
presenting_author <- function(authors_str, author_names_str) {
  fallback <- coalesce(
    str_trim(str_extract(authors_str, "^.+?\\)")),
    str_trim(str_extract(authors_str, "^[^;,]+"))
  )
  if (is.na(author_names_str) || is.na(authors_str)) {
    return(fallback)
  }
  names_parts <- str_split(author_names_str, ";\\s*")[[1]]
  authors_parts <- str_split(authors_str, ";\\s*")[[1]]
  idx <- which(str_detect(names_parts, "\\*"))[1]
  if (is.na(idx) || idx > length(authors_parts)) {
    return(fallback)
  }
  str_trim(authors_parts[idx])
}

# Append * after the presenting author's name (before their affiliation) in the
# full authors string so it displays in the rendered output.
mark_presenter <- function(authors_str, author_names_str) {
  if (is.na(author_names_str) || is.na(authors_str)) {
    return(authors_str)
  }
  names_parts <- str_split(author_names_str, ";\\s*")[[1]]
  authors_parts <- str_split(authors_str, ";\\s*")[[1]]
  idx <- which(str_detect(names_parts, "\\*"))[1]
  if (is.na(idx) || idx > length(authors_parts)) {
    return(authors_str)
  }
  entry <- str_trim(authors_parts[idx])
  entry <- if (str_detect(entry, "\\(")) {
    str_replace(entry, "\\s*\\(", "* (")
  } else {
    paste0(entry, "*")
  }
  authors_parts[idx] <- entry
  paste(str_trim(authors_parts), collapse = "; ")
}

# Helper function for proper title case (keeps articles/conjunctions/prepositions lowercase)
proper_title_case <- function(text) {
  if (is.na(text) || nchar(text) == 0) {
    return(text)
  }

  # Words that should be lowercase (unless first or last word)
  lowercase_words <- c(
    "a",
    "an",
    "and",
    "as",
    "at",
    "but",
    "by",
    "for",
    "from",
    "in",
    "into",
    "of",
    "on",
    "or",
    "the",
    "to",
    "with",
    "vs",
    "via"
  )

  # Split into words
  words <- str_split(text, "\\s+")[[1]]

  # Title case each word
  result <- map_chr(seq_along(words), function(i) {
    word <- words[i]
    word_lower <- str_to_lower(word)

    # Always capitalize first and last word
    if (i == 1 || i == length(words)) {
      return(str_to_title(word))
    }

    # Keep lowercase words lowercase
    if (word_lower %in% lowercase_words) {
      return(word_lower)
    }

    # Otherwise title case
    return(str_to_title(word))
  })

  return(paste(result, collapse = " "))
}

# Short track codes and colors
sessions <- sessions %>%
  mutate(
    track_short = case_when(
      category == "General Industry Studies" ~ "GIS",
      category ==
        "Health Care Systems, Biotechnology, and Pharmaceuticals" ~ "Health",
      category ==
        "Innovation, Entrepreneurship, and AI-Driven Transformation" ~ "Innovation",
      category ==
        "Labor Markets, Organizations, and the Future of Work" ~ "Labor",
      category ==
        "Operations, Supply Chain, and AI-Enhanced Industry 4.0" ~ "Operations",
      category == "Public Policy and Global Competitiveness" ~ "Policy",
      category ==
        "Sustainable Innovation, Energy, and Mobility" ~ "Sustainability",
      TRUE ~ "Panel"
    ),
    track_color = case_when(
      category == "General Industry Studies" ~ "gis",
      category ==
        "Health Care Systems, Biotechnology, and Pharmaceuticals" ~ "health",
      category ==
        "Innovation, Entrepreneurship, and AI-Driven Transformation" ~ "innovation",
      category ==
        "Labor Markets, Organizations, and the Future of Work" ~ "labor",
      category ==
        "Operations, Supply Chain, and AI-Enhanced Industry 4.0" ~ "operations",
      category == "Public Policy and Global Competitiveness" ~ "policy",
      category ==
        "Sustainable Innovation, Energy, and Mobility" ~ "sustainability",
      TRUE ~ "black"
    ),
    title = map_chr(title, proper_title_case)
  )
```

```{=latex}
\thispagestyle{empty}
\begin{center}
  \includegraphics[height=1.4in]{images/logo.png}
\end{center}
\vspace{0.6em}
\begin{center}
{\Huge\textbf{2026 Industry Studies Association}}\\[0.5em]
{\Huge\textbf{Annual Conference}}\\[1em]
{\Large\textit{Program Schedule}}\\[0.4em]
{\large June 3--5, 2026}\\[0.5em]
{\large George Washington University, Washington, DC}
\end{center}
\vspace{1em}
\noindent
\begin{minipage}[t]{0.48\textwidth}
  \includegraphics[width=\linewidth]{images/dc/dc_reflecting_pool.jpg}
\end{minipage}\hfill
\begin{minipage}[t]{0.48\textwidth}
  \includegraphics[width=\linewidth]{images/dc/dc_capitol.jpg}
\end{minipage}

\vspace{0.3em}
\noindent
\begin{minipage}[t]{0.48\textwidth}
  \includegraphics[width=\linewidth]{images/dc/dc_cherry_blossoms.jpg}
\end{minipage}\hfill
\begin{minipage}[t]{0.48\textwidth}
  \includegraphics[width=\linewidth]{images/dc/gwu_kogan_plaza.jpg}
\end{minipage}

\newpage
```

```{=latex}
\thispagestyle{plain.scrheadings}
\markboth{}{}
\pdfbookmark[0]{Scan QR Code}{qr}
\vspace*{\fill}
\begin{center}
  \includegraphics[width=2.5in]{images/qr-schedule.png}\\[1em]
  {\Large Scan to access the digital program}
\end{center}
\vspace*{\fill}
\newpage
```

```{=latex}
\thispagestyle{plain.scrheadings}
\markboth{}{}
\pdfbookmark[0]{Welcome}{welcome}
\begin{center}
{\Large\textbf{WELCOME!}}
\end{center}
\vspace{0.5em}
\noindent\textbf{\large John Gray, President of the Industry Studies Association}

\vspace{1em}

\begingroup
\raggedright
\begin{wrapfigure}{r}{0.28\textwidth}
  \vspace{-0.5em}
  \includegraphics[width=0.28\textwidth]{images/bios/john-gray.png}
  \vspace{-1em}
\end{wrapfigure}

Thank you for including the Industry Studies Association as part of your conference circuit. We are happy to welcome you to The George Washington University for an energizing few days of panels, paper sessions, plenaries and, most importantly, great side conversations.

Industry studies research is by its nature interdisciplinary, focused more on the interesting industry-specific phenomena and/or a policy dilemma. You may find yourself in a session diving deeply into a single industry from multiple perspectives, or one examining an issue across industries.

I want to thank John Paul Helveston ("JPH") for chairing the committee this year and serving as our host. He, along with a distinguished committee of local DC talent of Allison Forbes, Monica Gorman, David Hart, and Andrew Reamer helped to put together an amazing program, with many highlights including the Wednesday morning "excursion" into the world of DC entities that influence public policy. JPH also spearheaded the modernization of our program...he is the one to thank for our first ever searchable, online program app (he noted that he wanted to thank Claude Code for doing the lion's share!) and the thoughtful organization of the papers and special sessions.

I also want to recognize our program manager, Renae Sullivan, who is now just over a year into her job, for leading the great improvements you have probably noticed on our website, communication, and professionalism. While she is still our only paid employee, she has managed to spearhead many improvements. I also want to recognize our treasurer, Jeff Shockley. He (and Renae) worked many hours over the December-February time frame as we transitioned from outdated and clunky MemberClicks to our new, much easier to manage platform, Novi AMS. Taken together, we will soon be able to focus less on just executing the basics well but thinking creatively about ways to make more impact through membership growth, as well as additional partnerships and sources of funding.

I'll also note that, for the first time ever, we have a second major conference this year. Board member Benn Lawson has done a great job of organizing and promoting our first international conference, in Oxford, September 3-5. It will be every bit as large, if not larger, than this conference, and will grow our presence and influence outside of North America.

Finally, my term as president will end after this conference. I am delighted that founding member Ed Anderson from the University of Texas will take over - ISA is in good hands! I thank the entire board for working along with me for the last few years.

I can speak on behalf of the entire ISA board: We are very happy that you are here! We expect you will greatly enjoy the conference and hope that you will spread the word about ISA.

\vspace{2em}
\noindent John Gray\\
President, ISA
\endgroup
\newpage
```

```{=latex}
\thispagestyle{plain.scrheadings}
\markboth{}{}
\pdfbookmark[0]{Connecting to the Internet}{wifi}

\begin{center}
{\color{gwblue}\LARGE\textbf{Connecting to the Internet}}\\[0.2cm]
{\large\textbf{All Conference Venues}}\\[0.05cm]
{\color{darkgray} Science \& Engineering Hall · University Student Center (Marvin Center)}
\end{center}

\vspace{0.25cm}
\noindent\rule{\textwidth}{1.5pt}
\vspace{0.25cm}

\noindent\textbf{\large Option 1 — Guest WiFi (GWguest)}

\noindent For all conference attendees without a GW or eduroam account.

\vspace{0.2cm}

\begin{mdframed}[backgroundcolor=lightgray, linecolor=gwblue, linewidth=1.5pt, innerleftmargin=12pt, innerrightmargin=12pt, innertopmargin=7pt, innerbottommargin=7pt]
\begin{enumerate}
  \setlength{\itemsep}{3pt}
  \item Open your device's \textbf{WiFi settings} and select \textbf{GWguest}.
  \item If prompted with a certificate warning for \texttt{cppm.it.gwu.edu}, tap \textbf{Accept} or \textbf{Trust} (this is a GWU-issued certificate and is safe).
  \item Open a \textbf{web browser} — you will be automatically redirected to the self-registration page. If not, navigate to \texttt{my.gwu.edu}.
  \item Enter your name and email address to self-register. Access is valid for \textbf{72 hours}.
\end{enumerate}
\end{mdframed}

\vspace{0.35cm}

\noindent\textbf{\large Option 2 — eduroam (Academic Institutions)}

\noindent If your home institution participates in eduroam, you can connect directly.

\vspace{0.2cm}

\begin{mdframed}[backgroundcolor=lightgray, linecolor=gwgold, linewidth=1.5pt, innerleftmargin=12pt, innerrightmargin=12pt, innertopmargin=7pt, innerbottommargin=7pt]
\begin{enumerate}
  \setlength{\itemsep}{3pt}
  \item Open your device's \textbf{WiFi settings} and select \textbf{eduroam}.
  \item Sign in using your \textbf{home institution credentials} (e.g., \texttt{username@youruniversity.edu}).
  \item No additional registration is required.
\end{enumerate}
\end{mdframed}

\vspace{0.35cm}
\noindent\rule{\textwidth}{0.8pt}
\vspace{0.25cm}

\noindent\textbf{\large IT Support}

\vspace{0.15cm}

\begin{tabularx}{\textwidth}{lX}
\faPhone\quad \textbf{Help Desk} & 202-994-4948 \quad {\color{darkgray}(24/7)} \\[3pt]
\faPhone\quad \textbf{Classroom / AV} & 202-994-7900 \\[3pt]
\faEnvelope\quad \textbf{Email} & \texttt{ithelp@gwu.edu} \\[3pt]
\faGlobe\quad \textbf{Online} & \texttt{go.gwu.edu/ithelp} \\[3pt]
\faMapMarker*\quad \textbf{Walk-in} & Academic Center, 801 22nd St NW, Room B101 \\
\end{tabularx}

\vspace{0.3cm}
\noindent\rule{\textwidth}{0.8pt}
\newpage
```

```{=latex}
\thispagestyle{plain.scrheadings}
\markboth{}{}
\pdfbookmark[0]{Venue Map}{map}
{\Large\textbf{Map of conference locations at The George Washington University}}
\vspace{0.6em}

\begin{center}
  \includegraphics[width=\textwidth, height=0.72\textheight, keepaspectratio]{images/map.png}\\[0.6em]
  {\large On 6/3, please enter SEH Building at main entrance on H st \& 22nd}
\end{center}

\vspace{0.5em}
\begin{center}
  \includegraphics[width=1.4in]{images/qr-map.png}\\[0.4em]
  {\normalsize Scan for interactive Google map}
\end{center}
\newpage

\thispagestyle{plain.scrheadings}
\markboth{}{}
{\Large\textbf{Venue Floor Plans}}
\vspace{0.2em}

\begin{center}
  \includegraphics[width=\textwidth, height=0.42\textheight, keepaspectratio]{images/gh-seh-b1.png}\\[0.2em]
  {\normalsize\textit{Wednesday, June 3\\Classrooms on other floors will also be used for paper sessions}}
\end{center}

\vspace{0.1em}

\begin{center}
  \includegraphics[width=\textwidth, height=0.42\textheight, keepaspectratio]{images/gw-sc.png}\\[0.2em]
  {\normalsize\textit{Thursday, June 4 \& Friday, June 5\\All programming will be on the 3rd floor these days}}
\end{center}
\newpage
```

```{r}
#| label: awards-page
#| results: asis
awards <- read_csv(
  file.path('data', 'awards.csv'),
  show_col_types = FALSE
) %>%
  arrange(award_order, desc(rank == "Winner"))

cat("```{=latex}\n")
cat("\\markboth{}{}\n")
cat("\\pdfbookmark[0]{Award Winners}{awards}\n")
cat("\\noindent\\textbf{\\Large ISA 2026 Award Winners}\\par\n")
cat("\\vspace{0.5em}\n")
cat("{\\small\n")

current_award <- ""
current_awards_committee <- ""

for (i in seq_len(nrow(awards))) {
  r <- awards[i, ]

  if (r$award != current_award) {
    # Close previous award: print its committee
    if (current_award != "") {
      cat(
        "\\noindent\\textbf{Award Committee:} ",
        escape_latex(current_awards_committee),
        "\\par\n",
        sep = ""
      )
      cat("\\vspace{0.4em}\n\n")
    }
    # Page break before Gomory award
    if (r$award == "Ralph Gomory Best Industry Studies Paper Award") {
      cat("\\newpage\n")
    }
    # Open new award: name + description
    cat(
      "\\noindent\\textcolor{event}{\\textbf{",
      escape_latex(str_to_upper(r$award)),
      "}}\\par\\vspace{0.1em}\n",
      sep = ""
    )
    cat(
      "\\noindent\\textit{",
      escape_latex(r$description),
      "}\\par\\vspace{0.15em}\n",
      sep = ""
    )
    current_award <- r$award
    current_awards_committee <- coalesce(r$awards_committee, "")
  }

  rank_label <- if (r$rank == "Winner") {
    "\\textbf{Winner:}"
  } else {
    "\\textbf{Runner-up:}"
  }
  cat(
    "\\noindent ",
    rank_label,
    " \\textit{``",
    escape_latex(r$paper_title),
    "''}\\par\n",
    sep = ""
  )
  cat("\\noindent ", escape_latex(r$authors), "\\par\n", sep = "")

  if (!is.na(r$publication) && nchar(r$publication) > 0) {
    pub_line <- escape_latex(r$publication)
    if (!is.na(r$doi) && nchar(r$doi) > 0) {
      pub_line <- paste0(pub_line, ". ", escape_latex(r$doi))
    }
    cat("\\noindent\\textit{", pub_line, "}\\par\n", sep = "")
  }

  if (!is.na(r$committee) && nchar(r$committee) > 0) {
    cat(
      "\\noindent\\textit{Dissertation Committee: ",
      escape_latex(r$committee),
      "}\\par\n",
      sep = ""
    )
  }

  cat("\\vspace{0.2em}\n\n")
}

# Close the final award's committee
if (current_award != "") {
  cat(
    "\\noindent\\textbf{Award Committee:} ",
    escape_latex(current_awards_committee),
    "\\par\n",
    sep = ""
  )
}

cat("\\vspace{1.5em}\n\n")
cat(
  "\\begin{center}\\textbf{Join us Friday, June 6th at the awards luncheon, ",
  "when we will recognize all awardees.}\\end{center}\n",
  sep = ""
)

cat("}\n")
cat("\\newpage\n")
cat("```\n\n")
```

```{r}
#| label: conference-in-brief
#| results: asis
brief_data <- read_csv(
  file.path('data', 'overview.csv'),
  show_col_types = FALSE,
  col_types = cols(.default = "c")
) %>%
  rename_with(str_trim) %>%
  rename(
    weekday = Weekday,
    time_start_str = `Time Start`,
    time_end_str = `Time End`,
    session = Session,
    building = Building
  ) %>%
  mutate(
    weekday = str_trim(weekday),
    time_start_str = str_trim(time_start_str),
    time_end_str = str_trim(time_end_str),
    session = str_trim(session),
    building = str_trim(building),
    date_parsed = case_when(
      weekday == "Wednesday" ~ as.Date("2026-06-03"),
      weekday == "Thursday" ~ as.Date("2026-06-04"),
      weekday == "Friday" ~ as.Date("2026-06-05")
    ),
    start_dt = as.POSIXct(
      paste(format(date_parsed, "%Y-%m-%d"), time_start_str),
      format = "%Y-%m-%d %I:%M %p"
    ),
    time_fmt = paste0(
      str_replace_all(str_to_lower(time_start_str), " ", ""),
      "--",
      str_replace_all(str_to_lower(time_end_str), " ", "")
    ),
    is_highlighted = session %in%
      c(
        "Paper Sessions",
        "Concurrent Panel Sessions",
        "Opening Plenary",
        "PDW"
      )
  ) %>%
  arrange(date_parsed, start_dt)

days <- list(
  list(label = "WEDNESDAY, June 3", day = "Wednesday"),
  list(label = "THURSDAY, June 4", day = "Thursday"),
  list(label = "FRIDAY, June 5", day = "Friday")
)

cat("```{=latex}\n")
cat("\\markboth{}{}\n")
cat("\\pdfbookmark[0]{Conference in Brief}{brief}\n")
cat("\\noindent\\textbf{\\Large Conference in Brief}\\par\\vspace{0.5em}\n")
cat("{\\renewcommand{\\arraystretch}{0.9}\n")

# Registration section
cat(
  "\\noindent\\textcolor{event}{\\textbf{REGISTRATION}}\\par\\vspace{0.15em}\n"
)
cat("\\begin{tabular}{@{}p{3.2cm}p{\\dimexpr\\linewidth-3.5cm}@{}}\n")
cat(
  "  Wed., June 3 & 8:00am--6:00pm\\quad Science \\& Engineering Hall, B1 \\\\\n"
)
cat("  Wed., June 3 & 11:30am--2:00pm\\quad Milken Institute \\\\\n")
cat("  Thu.--Fri., June 4--5 & Student Center, 3rd Floor \\\\\n")
cat("\\end{tabular}\n")

for (d in days) {
  day_rows <- brief_data %>% filter(weekday == d$day)
  cat("\n\\vspace{0.5em}\n")
  cat(
    "\\noindent\\textcolor{event}{\\textbf{",
    escape_latex(d$label),
    "}}\\par\\vspace{0.15em}\n",
    sep = ""
  )
  cat("\\begin{tabular}{@{}p{3.2cm}p{\\dimexpr\\linewidth-3.5cm}@{}}\n")
  current_building <- ""
  for (i in seq_len(nrow(day_rows))) {
    r <- day_rows[i, ]
    bldg <- if (!is.na(r$building) && nchar(r$building) > 0) {
      r$building
    } else {
      current_building
    }
    if (bldg != current_building) {
      bldg_label <- bldg
      if (!is.na(r$excursion_id) && nchar(str_trim(r$excursion_id)) > 0) {
        room_val <- str_trim(r$Room)
        if (!is.na(room_val) && nchar(room_val) > 0) {
          bldg_label <- paste0(bldg, ", ", room_val)
        }
      }
      cat(
        "  \\multicolumn{2}{@{}l@{}}{\\textbf{",
        escape_latex(bldg_label),
        "}} \\\\\n",
        sep = ""
      )
      current_building <- bldg
    }
    session_text <- escape_latex(r$session)
    if (isTRUE(r$is_highlighted)) {
      session_text <- paste0("\\textcolor{event}{", session_text, "}")
    }
    cat("  ", r$time_fmt, " & ", session_text, " \\\\\n", sep = "")
  }
  cat("\\end{tabular}\n")
}

cat("}\n")
cat("\\newpage\n")
cat("```\n\n")
```

```{r}
#| label: morning-excursions
#| results: asis
excursions <- read_csv(
  file.path('data', 'overview.csv'),
  show_col_types = FALSE,
  col_types = cols(.default = "c")
) %>%
  rename_with(str_trim) %>%
  filter(!is.na(excursion_id)) %>%
  rename(
    id = excursion_id,
    option = excursion_option,
    session_name = Session,
    start_time = `Time Start`,
    end_time = `Time End`
  ) %>%
  mutate(option = as.integer(option)) %>%
  arrange(option)

excursion_program <- read_csv(
  file.path('data', 'excursion-program.csv'),
  show_col_types = FALSE
)

cat("```{=latex}\n")
cat("\\markboth{}{}\n")
cat("\\pdfbookmark[0]{Morning Excursions}{excursions}\n")
cat(
  "\\noindent\\textbf{\\Large Optional Morning Excursions}\\par\\vspace{0.3em}\n"
)
cat("\\noindent\\textit{Wednesday, June 3, 2026}\\par\\vspace{1em}\n")

for (i in seq_len(nrow(excursions))) {
  ex <- excursions[i, ]
  prog <- excursion_program %>% filter(excursion_id == ex$id)
  short_title <- sub("^Morning Excursion Option [0-9]+: ", "", ex$session_name)

  cat(
    "\\noindent\\textbf{\\large Option ",
    ex$option,
    ": ",
    escape_latex(short_title),
    "}\\par\\vspace{0.3em}\n",
    sep = ""
  )
  cat(
    "\\noindent{\\small\\textit{Meeting time:} ",
    escape_latex(ex$start_time),
    "\\quad\\textit{Meeting point:} ",
    escape_latex(ex$meeting_point),
    "}\\par\\vspace{0.5em}\n",
    sep = ""
  )
  if (!is.na(ex$description) && nchar(ex$description) > 0) {
    cat("\\noindent ", escape_latex(ex$description), "\\par\n", sep = "")
  }

  if (nrow(prog) > 0) {
    tl_rows <- prog %>% distinct(time_range, activity)
    spkr_rows <- prog %>% filter(!is.na(speaker_name) & speaker_name != "")

    cat("\\vspace{0.5em}\n")
    cat("\\noindent\\textbf{Program:}\\par\\vspace{0.3em}\n")
    cat("\\begin{tabular}{@{}l@{\\hspace{1.5em}}p{12cm}@{}}\n")
    for (t in seq_len(nrow(tl_rows))) {
      trow <- tl_rows[t, ]
      act <- trow$activity[[1]]
      org_spkr <- spkr_rows %>% filter(activity == act)
      is_org <- nrow(org_spkr) > 0

      # Org-visit rows: bold name, then panel title (italic) + speakers on new lines
      # \newline is the correct within-cell break for p{} columns (not \\)
      if (is_org) {
        cell <- paste0("\\textbf{", escape_latex(act), "}")
        pt <- org_spkr$org_panel_title[[1]]
        if (!is.na(pt) && nchar(pt) > 0) {
          cell <- paste0(
            cell,
            "\\newline{\\small\\textit{",
            escape_latex(pt),
            "}}"
          )
        }
        for (k in seq_len(nrow(org_spkr))) {
          cell <- paste0(
            cell,
            "\\newline{\\small\\hspace{1em}",
            escape_latex(org_spkr$speaker_name[[k]]),
            ", \\textit{",
            escape_latex(org_spkr$speaker_role[[k]]),
            "}}"
          )
        }
        row_end <- "\\\\[0.5em]\n"
      } else {
        cell <- escape_latex(act)
        row_end <- "\\\\\n"
      }

      cat(
        "{\\small\\texttt{",
        escape_latex(trow$time_range[[1]]),
        "}}",
        " & ",
        cell,
        row_end,
        sep = ""
      )
    }
    cat("\\end{tabular}\\par\n")
  }

  if (i < nrow(excursions)) cat("\\vspace{1.5em}\n\n")
}

cat("\\newpage\n")
cat("```\n\n")
```

```{=latex}
\markboth{}{}
\pdfbookmark[0]{Research Streams}{streams}
\noindent\textbf{\large Research stream descriptions, abbreviations, and color key:}

\vspace{1.2em}

\noindent\textbf{\textcolor{sustainability}{1. Energy, Sustainable Innovation, and Mobility (EN)}}

\vspace{0.3em}
\noindent This stream invites papers and panels on the changing market and public policy landscape where the energy industry (including oil and gas, electricity, pipelines) intersects with environmental concerns.

\vspace{1em}

\noindent\textbf{\textcolor{gis}{2. General Industry Studies (GO)}}

\vspace{0.3em}
\noindent Any research on issues or industries not covered in other research streams described above may be submitted to this general stream. Papers or organized panels comparing phenomena, trends, issues, or economic activities across occupations, industries, or geographic regions are especially welcome.

\vspace{1em}

\noindent\textbf{\textcolor{health}{3. Health Care Systems, Biotechnology, and Pharmaceuticals (HC)}}

\vspace{0.3em}
\noindent This stream invites papers and panels that examine the myriad of issues surrounding effective management of health care entities and systems (e.g., hospitals, medical groups, public health agencies, insurance companies, pharmaceutical firms, technology companies, etc.).

\vspace{1em}

\noindent\textbf{\textcolor{innovation}{4. Innovation, Entrepreneurship, and AI-Driven Transformation (IE)}}

\vspace{0.3em}
\noindent This stream invites papers and panels that examine innovation within firms and other organizations such as universities, across organizational boundaries, across country boundaries, and in new entrepreneurial ventures.

\vspace{1em}

\noindent\textbf{\textcolor{labor}{5. Labor Markets, Organizations, and the Future of Work (LM)}}

\vspace{0.3em}
\noindent This stream welcomes papers and panels that examine the impacts of firm, industry, and market characteristics on labor markets, industrial relations, and/or human resource practices as well as public policy outcomes.

\vspace{1em}

\noindent\textbf{\textcolor{operations}{6. Operations, Supply Chain, and AI-Enhanced Industry 4.0 (OP)}}

\vspace{0.3em}
\noindent This stream welcomes papers and panels that are concerned with the oversight, design, and control of the business processes responsible for the production of goods and services as well as those focused on coordination of (multiple) firms responsible for these business processes within a supply network.

\vspace{1em}

\noindent\textbf{\textcolor{policy}{7. Public Policy, and Global Competitiveness (PP)}}

\vspace{0.3em}
\noindent Public policy -- whether national, regional, local or global -- often shapes opportunities for industries, including competitive options within industries and globalization of industries. In turn, wrestling with these opportunities, competitiveness and globalization have had a profound impact on the nature of industrial activity and policy.

\newpage
```

```{r}
#| label: special-session-descriptions
#| results: asis
bios <- read_csv(
  file.path('data', 'bios.csv'),
  show_col_types = FALSE
)

bio_panels <- read_csv(
  file.path('data', 'bio-panels.csv'),
  show_col_types = FALSE
)

panel_order_ids <- panels_raw %>%
  arrange(start_dt, id) %>%
  pull(id)

cat("```{=latex}\n")
cat("\\markboth{Special Session Descriptions}{}\n")
cat("\\pdfbookmark[0]{Special Session Descriptions}{specsessions}\n")
cat(
  "\\noindent\\textbf{\\Large Special Session Descriptions}\\par\\vspace{0.8em}\n\n"
)

seen_people <- character(0)
first_panel <- list()
current_day <- ""

for (pid in panel_order_ids) {
  p <- panels_raw %>% filter(id == pid)
  spkrs <- bio_panels %>% filter(panel_id == pid) %>% arrange(panel_order)

  if (nrow(spkrs) == 0) {
    next
  }

  day_label <- if (p$date_parsed[[1]] == as.Date("2026-06-03")) {
    "Wednesday, June 3"
  } else if (p$date_parsed[[1]] == as.Date("2026-06-04")) {
    "Thursday, June 4"
  } else {
    "Friday, June 5"
  }

  if (day_label != current_day) {
    if (current_day != "") {
      cat("\\newpage\n\n")
    }
    cat(
      "\\noindent{\\large\\textbf{",
      escape_latex(day_label),
      "}}\\par\n",
      sep = ""
    )
    cat(
      "\\vspace{0.3em}\\noindent\\rule{\\linewidth}{0.5pt}\\par\\vspace{0.8em}\n\n",
      sep = ""
    )
    current_day <- day_label
  } else {
    cat("\\newpage\n\n")
  }

  time_str <- paste0(
    sub("^0", "", format(p$start_dt[[1]], "%I:%M %p")),
    " – ",
    sub("^0", "", format(p$end_dt[[1]], "%I:%M %p"))
  )

  cat(
    "\\noindent{\\large\\textbf{\\textcolor{",
    p$track_color[[1]],
    "}{",
    escape_latex(p$title[[1]]),
    "}}}\\\\[0.2em]\n",
    sep = ""
  )
  cat(
    "{\\small\\textit{",
    escape_latex(time_str),
    " $\\cdot$ Room ",
    escape_latex(p$room[[1]]),
    "}}\\par\\vspace{0.5em}\n",
    sep = ""
  )

  desc <- p$description[[1]]
  if (!is.na(desc) && str_trim(desc) != "" && str_trim(desc) != "TBD") {
    cat("{\\small ", escape_latex(desc), "}\\par\\vspace{0.8em}\n\n", sep = "")
  }

  has_mod <- any(spkrs$role == "moderator")
  mod_done <- FALSE
  pan_done <- FALSE

  for (i in seq_len(nrow(spkrs))) {
    spk <- spkrs[i, ]
    person <- bios %>% filter(person_id == spk$person_id)

    if (nrow(person) == 0) {
      next
    }

    is_repeat <- spk$person_id %in% seen_people

    if (spk$role == "moderator" && !mod_done) {
      cat(
        "\\noindent{\\small\\textit{Moderator:}}\\par\\vspace{0.3em}\n\n",
        sep = ""
      )
      mod_done <- TRUE
    } else if (spk$role == "panelist" && !pan_done) {
      if (mod_done) {
        cat("\\par\\vspace{0.3em}\n")
      }
      cat(
        "\\noindent{\\small\\textit{Panelists:}}\\par\\vspace{0.3em}\n\n",
        sep = ""
      )
      pan_done <- TRUE
    }

    image_id <- if (nrow(person) > 0 && !is.na(person$image[[1]])) str_trim(person$image[[1]]) else ""
    img_path <- file.path("images", "bios", paste0(image_id, ".png"))
    has_image <- image_id != "" && file.exists(img_path)

    cat("\\noindent%\n")
    if (has_image) {
      cat("\\begin{minipage}[t]{1.1in}\n")
      cat(
        "  \\vspace{0pt}\\includegraphics[width=1.1in]{",
        img_path,
        "}\n",
        sep = ""
      )
      cat("\\end{minipage}%\n")
      cat("\\hspace{0.15in}%\n")
      cat("\\begin{minipage}[t]{\\dimexpr\\linewidth-1.25in\\relax}\n")
    } else {
      cat("\\begin{minipage}[t]{\\linewidth}\n")
    }
    cat("  \\vspace{0pt}%\n")
    cat(
      "  \\textbf{",
      escape_latex(person$name[[1]]),
      "}\\par\\vspace{0.2em}\n",
      sep = ""
    )

    if (!is_repeat) {
      cat("  {\\small ", escape_latex(person$bio[[1]]), "}\\par\n", sep = "")
      seen_people <- c(seen_people, spk$person_id)
      first_panel[[spk$person_id]] <- p$title[[1]]
    } else {
      short_desc <- str_extract(person$bio[[1]], "^[^.]+\\.")
      cat(
        "  {\\small ",
        escape_latex(short_desc),
        "}\\par\\vspace{0.15em}\n",
        sep = ""
      )
      ref <- first_panel[[spk$person_id]]
      if (!is.null(ref)) {
        cat(
          "  {\\small\\textit{(Full bio appears above under ``",
          escape_latex(ref),
          "''.)}}\\par\n",
          sep = ""
        )
      }
    }

    cat("\\end{minipage}%\n")
    cat("\\par\\vspace{0.9em}\n\n")
  }
}

cat("\\newpage\n")
cat("```\n\n")
```

```{r}
#| label: schedule
#| results: asis
# Build award lookup: normalize titles and map to {award, rank}
normalize_title <- function(t) {
  t %>%
    str_to_lower() %>%
    str_trim() %>%
    str_replace_all("\u2018|\u2019", "'") %>%
    str_replace_all("\u201c|\u201d", '"')
}

awards_lookup <- read_csv(
  file.path('data', 'awards.csv'),
  show_col_types = FALSE,
  col_types = cols(.default = "c")
) %>%
  select(paper_title, award, rank) %>%
  mutate(norm_title = normalize_title(paper_title))

get_award_label <- function(title) {
  norm <- normalize_title(title)
  m <- awards_lookup %>%
    filter(
      norm_title == norm |
        startsWith(norm, norm_title) |
        startsWith(norm_title, norm)
    )
  if (nrow(m) == 0) {
    return("")
  }
  r <- m$rank[1]
  award_name <- m$award[1]
  short_name <- escape_latex(award_name)
  if (r == "Winner") {
    paste0(
      " \\textcolor{awardgold}{\\small\\,$\\star$ \\textit{Winner: ",
      short_name,
      "}}"
    )
  } else {
    paste0(
      " \\textcolor{gray}{\\small\\,$\\star$ \\textit{Runner-up: ",
      short_name,
      "}}"
    )
  }
}

# Build paper time blocks (one per time slot)
paper_blocks <- sessions %>%
  filter(!is.na(time_slot)) %>%
  group_by(time_slot) %>%
  summarize(
    day_name = first(day),
    start_dt = as.POSIXct(paste(first(as.character(date)), first(start_time))),
    end_dt = as.POSIXct(paste(first(as.character(date)), first(end_time))),
    .groups = "drop"
  ) %>%
  mutate(block_type = "paper", block_key = time_slot)

# Build panel time blocks (one per unique start time)
panel_blocks <- panels_raw %>%
  group_by(start_dt, end_dt, day_name) %>%
  summarize(.groups = "drop") %>%
  arrange(start_dt) %>%
  mutate(block_type = "panel", block_key = paste0("PANEL_", row_number()))

# Build event blocks (breaks, meals, receptions)
event_blocks <- overview_events %>%
  arrange(start_dt) %>%
  mutate(block_type = "event", block_key = paste0("EV", row_number())) %>%
  select(block_type, block_key, day_name, start_dt, end_dt, session_name, room)

# Combine all blocks and sort chronologically
all_blocks <- bind_rows(
  paper_blocks %>%
    select(block_type, block_key, day_name, start_dt, end_dt) %>%
    mutate(event_name = NA_character_, event_room = NA_character_),
  panel_blocks %>%
    select(block_type, block_key, day_name, start_dt, end_dt) %>%
    mutate(event_name = NA_character_, event_room = NA_character_),
  event_blocks %>%
    rename(event_name = session_name, event_room = room) %>%
    select(
      block_type,
      block_key,
      day_name,
      start_dt,
      end_dt,
      event_name,
      event_room
    )
) %>%
  arrange(start_dt, block_type)

# Read all overview rows (no filter) for day overview pages
all_overview <- read_csv(
  file.path('data', 'overview.csv'),
  show_col_types = FALSE,
  col_types = cols(.default = "c")
) %>%
  rename_with(str_trim) %>%
  rename(
    weekday = Weekday,
    time_start_str = `Time Start`,
    time_end_str = `Time End`,
    session = Session,
    building = Building,
    room_raw = Room
  ) %>%
  mutate(
    weekday = str_trim(weekday),
    time_start_str = str_trim(time_start_str),
    time_end_str = str_trim(time_end_str),
    session = str_trim(session),
    building = str_trim(coalesce(building, "")),
    room_raw = str_trim(str_replace_all(coalesce(room_raw, ""), "\\s+", " ")),
    date_parsed = case_when(
      weekday == "Wednesday" ~ as.Date("2026-06-03"),
      weekday == "Thursday" ~ as.Date("2026-06-04"),
      weekday == "Friday" ~ as.Date("2026-06-05")
    ),
    start_dt = as.POSIXct(
      paste(format(date_parsed, "%Y-%m-%d"), time_start_str),
      format = "%Y-%m-%d %I:%M %p"
    ),
    time_fmt = paste0(
      str_replace_all(str_to_lower(time_start_str), " ", ""),
      "--",
      str_replace_all(str_to_lower(time_end_str), " ", "")
    ),
    location = case_when(
      nchar(building) > 0 & nchar(room_raw) > 0 ~ paste(
        building,
        room_raw,
        sep = ", "
      ),
      nchar(building) > 0 ~ building,
      TRUE ~ room_raw
    )
  ) %>%
  arrange(date_parsed, start_dt)

day_labels <- c(
  "Wednesday" = "Wednesday, June 3",
  "Thursday" = "Thursday, June 4",
  "Friday" = "Friday, June 5"
)

emit_day_overview <- function(day_name) {
  label <- day_labels[[day_name]]
  day_data <- all_overview %>% filter(weekday == day_name)
  day_anchor <- paste0("day-", gsub("[^a-zA-Z]", "", tolower(day_name)))
  cat("```{=latex}\n")
  cat("\\markboth{}{}\n")
  cat(
    "\\pdfbookmark[0]{",
    escape_latex(label),
    "}{",
    day_anchor,
    "}\n",
    sep = ""
  )
  cat(
    "\\noindent\\colorbox{event}{\\parbox{\\dimexpr\\linewidth-2\\fboxsep}{",
    "\\centering\\textcolor{white}{\\large\\textbf{Conference Program: ",
    escape_latex(label),
    "}}}}\n\n",
    sep = ""
  )
  cat("\\vspace{0.6em}\n\n")
  cat("{\\renewcommand{\\arraystretch}{0.9}\n\n")
  for (i in seq_len(nrow(day_data))) {
    r <- day_data[i, ]
    cat(
      "\\noindent\\textcolor{event}{\\textbf{",
      escape_latex(str_to_upper(r$session)),
      "}}\n\n",
      sep = ""
    )
    cat("\\begin{tabular}{@{}p{3.2cm}p{\\dimexpr\\linewidth-3.5cm}@{}}\n")
    cat("  ", r$time_fmt, " & ", escape_latex(r$location), " \\\\\n", sep = "")
    cat("\\end{tabular}\n\n")
    cat("\\vspace{0.25em}\n\n")
  }
  cat("}\n")
  cat("\\newpage\n")
  cat("```\n\n")
}

current_day <- ""

for (b in seq_len(nrow(all_blocks))) {
  block <- all_blocks[b, ]

  if (block$day_name != current_day) {
    # New day: emit one-page day overview, then render first block without extra break
    if (current_day != "") {
      cat("\n\\newpage\n\n")
    }
    emit_day_overview(block$day_name)
    current_day <- block$day_name
  } else {
    # Same day: regular page break logic
    prev_block <- all_blocks[b - 1, ]
    if (block$block_type != "event" && prev_block$block_type != "event") {
      cat("\n\\newpage\n\n")
    } else if (
      block$block_type != "event" && isTRUE(prev_block$event_name == "PDW")
    ) {
      cat("\n\\newpage\n\n")
    } else {
      cat("\n\\vspace{1em}\n\n")
    }
  }

  # Day label used in running header marks
  day_label <- switch(
    block$day_name,
    "Wednesday" = "Wednesday, June 3",
    "Thursday" = "Thursday, June 4",
    "Friday" = "Friday, June 5",
    block$day_name
  )

  # Event blocks: compact colored box, no page header
  if (block$block_type == "event") {
    time_label <- paste0(
      format(block$start_dt, "%I:%M %p"),
      " – ",
      format(block$end_dt, "%I:%M %p")
    )
    cat(
      "\\markboth{",
      escape_latex(day_label),
      "}{",
      escape_latex(block$event_name),
      "}\n\n",
      sep = ""
    )
    cat("\\begin{center}\n")
    cat(
      "\\colorbox{event!15}{\\parbox{0.9\\linewidth}{\\centering\n",
      "  \\textcolor{event}{\\large\\textbf{",
      escape_latex(block$event_name),
      "}}\\\\[2pt]\n",
      "  {\\small ",
      block$day_name,
      ", ",
      time_label,
      " $\\cdot$ \\textit{",
      escape_latex(block$event_room),
      "}}\n",
      "}}\n",
      sep = ""
    )
    cat("\\end{center}\n\n")
    next
  }

  # Session type label and time header — centered (paper / panel blocks)
  is_plenary_block <- block$block_type == "panel" &&
    "P1" %in% (panels_raw %>% filter(start_dt == block$start_dt) %>% pull(id))

  session_type <- if (is_plenary_block) {
    "Plenary Session"
  } else if (block$block_type == "paper") {
    "Paper Sessions"
  } else {
    "Special Sessions"
  }

  time_label <- paste0(
    block$day_name,
    ", ",
    format(block$start_dt, "%I:%M %p"),
    " – ",
    format(block$end_dt, "%I:%M %p")
  )

  bm_anchor <- paste0("slot-", gsub("[^a-zA-Z0-9]", "", block$block_key))
  bm_label <- paste0(
    session_type,
    ": ",
    format(block$start_dt, "%I:%M %p"),
    " -- ",
    format(block$end_dt, "%I:%M %p")
  )
  cat("\\pdfbookmark[1]{", bm_label, "}{", bm_anchor, "}\n\n", sep = "")

  cat(
    "\\markboth{",
    escape_latex(day_label),
    "}{",
    session_type,
    " | ",
    format(block$start_dt, "%I:%M %p"),
    " – ",
    format(block$end_dt, "%I:%M %p"),
    "}\n\n",
    sep = ""
  )
  cat("\\begin{center}\n")
  cat("\\normalsize\\textit{", session_type, "}\\\\[0.3em]\n", sep = "")
  cat("\\Large\\textbf{", time_label, "}\n", sep = "")
  cat("\\end{center}\n\n")

  if (block$block_type == "paper") {
    ts <- block$block_key
    ts_sessions <- sessions %>%
      filter(time_slot == ts)

    # Get unique categories in this time slot, alphabetically
    track_order <- sort(unique(ts_sessions$category))

    # Loop through categories
    for (cat_name in track_order) {
      cat_sessions <- ts_sessions %>%
        filter(category == cat_name) %>%
        arrange(room)

      if (nrow(cat_sessions) == 0) {
        next
      }

      track_color <- unique(cat_sessions$track_color)[1]

      # Get unique sessions within this category
      unique_sess <- cat_sessions %>%
        distinct(session_id, session_name, room, is_panel) %>%
        arrange(room)

      for (k in seq_len(nrow(unique_sess))) {
        s <- unique_sess[k, ]

        # Repeat category header for each session
        cat("\n## \\textcolor{", track_color, "}{", cat_name, "}\n\n", sep = "")

        # Get session data
        session_data <- cat_sessions %>%
          filter(session_id == s$session_id)

        # Panel tag for panel discussion sessions only
        panel_tag <- if (s$is_panel) {
          " *(Panel Discussion)*"
        } else {
          ""
        }

        # Session title with room
        cat(
          "\n**",
          escape_latex(s$session_name),
          "**",
          panel_tag,
          " — Room ",
          s$room,
          "\n\n",
          sep = ""
        )

        if (s$is_panel) {
          # For panel sessions: show description and participants
          panel_info <- session_data %>%
            select(panel_description, authors) %>%
            slice(1)

          # Show panel description if available
          if (
            !is.na(panel_info$panel_description) &&
              nchar(panel_info$panel_description) > 0
          ) {
            cat(escape_latex(panel_info$panel_description), "\n\n")
          }

          # Show participants
          cat("**Participants:**\n\n")
          authors_list <- session_data %>%
            select(authors) %>%
            distinct()

          for (m in seq_len(nrow(authors_list))) {
            cat("- ", escape_latex(authors_list$authors[m]), "\n")
          }
          cat("\n")
        } else {
          # For regular sessions: show paper list in sessions/*.csv row order
          papers <- session_data %>%
            arrange(paper_order) %>%
            select(authors, author_names, title)

          # Session chair: presenting author (*) of first paper, else first author
          session_chair <- presenting_author(
            papers$authors[1],
            papers$author_names[1]
          )
          if (!is.na(session_chair) && nchar(session_chair) > 0) {
            cat(
              "**Session Chair:** ",
              escape_latex(session_chair),
              "\n\n",
              sep = ""
            )
          }

          for (m in seq_len(nrow(papers))) {
            display_authors <- mark_presenter(
              papers$authors[m],
              papers$author_names[m]
            )
            cat(
              m,
              ". **",
              escape_latex(display_authors),
              "** — ",
              escape_latex(papers$title[m]),
              get_award_label(papers$title[m]),
              "\n\n",
              sep = ""
            )
          }

          # Discussant (self-organized sessions only)
          disc <- unique(na.omit(session_data$discussant))
          if (length(disc) > 0 && nchar(disc[1]) > 0) {
            cat("**Discussant:** ", escape_latex(disc[1]), "\n\n", sep = "")
          }
        }
      }
    }
  } else {
    # Panel block: render each panel in this time group
    group_panels <- panels_raw %>%
      filter(start_dt == block$start_dt) %>%
      arrange(category, room)

    for (k in seq_len(nrow(group_panels))) {
      p <- group_panels[k, ]

      cat(
        "\n## \\textcolor{",
        p$track_color,
        "}{",
        escape_latex(p$category),
        "}\n\n",
        sep = ""
      )

      cat(
        "\n**",
        escape_latex(p$title),
        "** *(Panel Discussion)*",
        " — Room ",
        escape_latex(p$room),
        "\n\n",
        sep = ""
      )

      # Moderator
      mod <- str_trim(p$moderator)
      if (!is.na(mod) && nchar(mod) > 0 && mod != "TBD") {
        cat("**Moderator:** ", escape_latex(mod), "\n\n", sep = "")
      }

      # Panelists
      pan_raw <- p$panelists
      if (
        !is.na(pan_raw) && str_trim(pan_raw) != "" && str_trim(pan_raw) != "TBD"
      ) {
        panelist_list <- str_split(pan_raw, "\n")[[1]] %>%
          str_trim() %>%
          .[nchar(.) > 0]
        cat("**Panelists:**\n\n")
        for (pan in panelist_list) {
          cat("- ", escape_latex(pan), "\n")
        }
        cat("\n")
      }
    }
  }
}
```

```{=latex}
\newpage
\thispagestyle{plain.scrheadings}
\markboth{}{}
\pdfbookmark[0]{Sponsors}{sponsors}
\vspace*{\fill}
\begin{center}
  {\Large\textbf{Thank You to Our Sponsors}}
\end{center}
\vspace{1.2em}
\begin{center}
  \begin{tabular}{ccc}
    \makebox[1.9in][c]{\includegraphics[width=1.9in,height=1.0in,keepaspectratio]{images/sponsors/byu-marriot.png}} &
    \makebox[1.9in][c]{\includegraphics[width=1.9in,height=1.0in,keepaspectratio]{images/sponsors/cambridge.png}} &
    \makebox[1.9in][c]{\includegraphics[width=1.9in,height=1.0in,keepaspectratio]{images/sponsors/gwu.png}} \\[2em]
    \makebox[1.9in][c]{\includegraphics[width=1.9in,height=1.0in,keepaspectratio]{images/sponsors/said-oxford.png}} &
    \makebox[1.9in][c]{\includegraphics[width=1.9in,height=1.0in,keepaspectratio]{images/sponsors/vcu-business.jpg}} &
    \makebox[1.9in][c]{\includegraphics[width=1.9in,height=1.0in,keepaspectratio]{images/sponsors/wsb-madison.png}} \\
  \end{tabular}
\end{center}
\vspace*{\fill}
\newpage
```

```{r}
#| label: committee-page
#| results: asis
committee <- read_csv(
  file.path('data', 'committee.csv'),
  show_col_types = FALSE
) %>%
  arrange(sort_order)

board <- committee %>% filter(group == "board")
iscc_grp <- committee %>% filter(group == "iscc")
streams <- committee %>% filter(group == "stream_chairs")

make_rows <- function(df) {
  rows <- vapply(
    seq_len(nrow(df)),
    function(i) {
      nm <- escape_latex(df$name[i])
      rol <- escape_latex(df$role[i])
      aff <- escape_latex(df$affiliation[i])
      sep <- if (i < nrow(df)) " \\\\[0.2em]\n" else " \\\\\n"
      paste0("  \\textbf{", nm, "} & \\textit{", rol, ", ", aff, "}", sep)
    },
    character(1)
  )
  paste(rows, collapse = "")
}

make_stream_rows <- function(df) {
  rows <- vapply(
    seq_len(nrow(df)),
    function(i) {
      nm <- escape_latex(df$name[i])
      rol <- escape_latex(df$role[i])
      aff <- escape_latex(df$affiliation[i])
      sep <- if (i < nrow(df)) " \\\\[0.2em]\n" else " \\\\\n"
      paste0("  \\textbf{", rol, "}---", nm, " & \\textit{", aff, "}", sep)
    },
    character(1)
  )
  paste(rows, collapse = "")
}

cat("```{=latex}\n")
cat("\\newpage\n")
cat("\\thispagestyle{plain.scrheadings}\n")
cat("\\markboth{}{}\n")
cat("\\pdfbookmark[0]{ISA Leadership}{leadership}\n\n")
cat("{\\large\\textbf{\\underline{Board of Directors}}}\\\\[0.6em]\n")
cat("{\\small\n\\begin{tabular}{lp{0.60\\textwidth}}\n")
cat(make_rows(board))
cat("\\end{tabular}\n}\n\n")
cat("\\vspace{1.2em}\n")
cat(
  "{\\large\\textbf{\\underline{Industry Studies Conference Committee (ISCC)}}}\\\\[0.6em]\n"
)
cat("{\\small\n\\begin{tabular}{lp{0.60\\textwidth}}\n")
cat(make_rows(iscc_grp))
cat("\\end{tabular}\n}\n\n")
cat("\\vspace{0.8em}\n")
cat("{\\large\\textbf{\\underline{Research Stream Chairs}}}\\\\[0.6em]\n")
cat("{\\small\n\\begin{tabular}{lp{0.58\\textwidth}}\n")
cat(make_stream_rows(streams))
cat("\\end{tabular}\n}\n")
cat("```\n")
```

```{=latex}
\thispagestyle{plain.scrheadings}
\markboth{}{}
\pdfbookmark[0]{ISA 2026 International Conference}{isa2026intl}
\vspace*{\fill}
\begin{center}
  {\Large\textbf{Join Us At Our First International Conference This Fall!}}\\[0.8em]
  {\large Sa\"{i}d Business School, Oxford University $\bullet$ September 3 - 5, 2026 $\bullet$ Oxford, UK}\\[2em]
  \includegraphics[height=2in]{images/sponsors/said-oxford.png}\\[1.5em]
  \includegraphics[width=\textwidth, keepaspectratio]{images/oxford.png}
\end{center}
\vspace*{\fill}
```

```{=latex}
\newpage
```

```{=latex}
\thispagestyle{plain.scrheadings}
\markboth{}{}
\pdfbookmark[0]{ISA 2027}{isa2027}
\begin{center}
  {\Large\textbf{Join Us Next Year!}}\\[0.8em]
  {\LARGE\textbf{ISA 2027 Annual Conference}}\\[0.5em]
  {\large Brigham Young University $\bullet$ May 26 - 28, 2027 $\bullet$ Provo, Utah}\\[1em]
  \includegraphics[height=0.8in]{images/byu-logo.png}
\end{center}
\vspace{0.6em}
\noindent
\includegraphics[width=\textwidth, keepaspectratio]{images/byu-pano.png}
\vspace{0.3em}
\noindent
\begin{minipage}[t]{0.31\textwidth}
  \includegraphics[width=\linewidth]{images/byu-campus.png}
\end{minipage}\hfill
\begin{minipage}[t]{0.31\textwidth}
  \includegraphics[width=\linewidth]{images/byu-bridge.png}
\end{minipage}\hfill
\begin{minipage}[t]{0.31\textwidth}
  \includegraphics[width=\linewidth]{images/byu-sign.png}
\end{minipage}
```
